smooth-sea

### 2018-06-03 index.rmd
trying sub-pages for html files

---
title: "smooth-sea"
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - { title: "hesscl.com", href: "http://hesscl.com", align: right ,
          title: "Manuscript", href: "http://github.com/hesscl/smooth-sea/smooth-sea.html", align: right}
    orientation: columns
    theme: bootstrap
    logo: logo.svg
    source_code: "https://github.com/hesscl/smooth-sea"
---

@@

This website provides interactive results for the forecasting models explored in the paper [_Estimating Neighborhood Asking Rents using Scraped Craigslist Rental Listings_](http://github.com/hesscl/smooth-sea/smooth-sea.html).

>>>>

---
title: "smooth-sea"
output: 
  flexdashboard::flex_dashboard:
    navbar:
       - {title: "hesscl.com", href: "http://hesscl.com", align: right} 
    orientation: columns
    theme: bootstrap
    logo: logo.svg
    source_code: "https://github.com/hesscl/smooth-sea"
---

@@

This website provides interactive results for the forecasting models explored in the paper _Estimating Neighborhood Asking Rents using Scraped Craigslist Rental Listings_.
